---
title: "Evaluating A DiD Study: Land Titling in Ecuador"
format: pdf
date: "2026-03-06"
author: "Jaslyn Miura, Isabella Segarra, Richie Montes Lemus"
---

## About our Replication:  

An R script that runs the analyses made in the study was publicly available along with the associated study data. While the code provided a framework for us to replicate the study, we’ve refactored and tidy-ed the code to make it more reproducible. We’ve also implemented different analysis methods within our replication due to the scale of the data, as authors have warned that the some aspects of the original code has long run times (over 10+ hours). Our approach in our replication is to implement the methods we’ve learned in class to compare our results to the original study, to further understand and justify the methodological steps made by authors.

[Original analysis R code can be found here](https://dataverse.harvard.edu/file.xhtml?persistentId=doi:10.7910/DVN/GT6EJJ/GPFQWQ&version=1.0&toolType=PREVIEW).

## Data

```{r, message=FALSE, warning=FALSE}
# Load in necessary Libraries
library(tidyverse)
library(dplyr)
library(MatchIt)
```

```{r, message=FALSE}
# Read in the data.
data <- read_csv(here::here("data", "BHM_sample20.csv"))

# Treatment variables
data$PML <- ifelse(data$A352 == 0, 0, 1)
data$PMI <- ifelse(data$A352 >= 3, 1, 0) #Note: all PSUR intervention had PMI in 2003 and after
names(data)[287:298] <- c("fl.2001", "fl.2002", "fl.2003", "fl.2004", "fl.2005", 
                          "fl.2006", "fl.2007", "fl.2008", "fl.2009", "fl.2010", 
                          "fl.2011", "fl.2012")
data$toPeru.km <- data$A486/1000

# This function remakes the data frame with only the specified columns & NAs removed:
make <- function(data, names) {
  # capture unquoted variable names.
  vars <- as.character(substitute(names))[-1]
  # Subset and remove NA rows.
  data.make <- data[, vars, drop = FALSE]
  data.make <- na.omit(data.make)
  # Print number of observations.
  cat("ob =", nrow(data.make), "\n")

  return(data.make)
}
```

```{r}
# Cleaning the datasets based on years within the study time frame.

wave_2002 <- data %>%
  # Keep A352 == 0 or 2
  filter(A352 %in% c(0, 2)) %>%
  mutate(
    # Post PML totals + each year
    fl_5yr_postPML = fl.2003 + fl.2004 + fl.2005 + fl.2006 + fl.2007,
    fl_yr1 = fl.2003,
    fl_yr2 = fl.2004,
    fl_yr3 = fl.2005,
    fl_yr4 = fl.2006,
    fl_yr5 = fl.2007,
    # Pre vars
    fl_pre_5cell = fl.2001 + A393 + A461,
    # Same as wave.2002[,314] - wave.2002[,287]
    forest_pre = .[[314]] - .[[287]],
    pop_den_1km_pre  = A173,
    pop_den_5km_pre  = A176,
    pop_den_10km_pre = A174,
    dist_disturb_pre = A116,
    wave = "two") %>%
  # Final filters
  filter(forest_pre > 450000, A346 == 0)

wave_2003 <- data %>%
  filter(A352 %in% c(0, 3)) %>%
  mutate(
    # 5-year post-PML sum + each year
    fl_5yr_postPML = fl.2004 + fl.2005 + fl.2006 + fl.2007 + fl.2008,
    fl_yr1 = fl.2004,
    fl_yr2 = fl.2005,
    fl_yr3 = fl.2006,
    fl_yr4 = fl.2007,
    fl_yr5 = fl.2008,
    # Pre variables
    fl_pre_5cell = fl.2002 + A394 + A462,
    # Forest.pre = col314 - rowSums(cols 287:288)
    forest_pre = .[[314]] - rowSums(across(all_of(287:288)), na.rm = TRUE),
    pop_den_1km_pre  = A178,
    pop_den_5km_pre  = A181,
    pop_den_10km_pre = A179,
    dist_disturb_pre = A117,
    wave = "three") %>%
  filter(forest_pre > 450000, A346 == 0)

wave_2004 <- data %>%
  filter(A352 == 0) %>%
  mutate(
    # 5-year post-PML sum + each year
    fl_5yr_postPML = rowSums(across(fl.2005:fl.2009), na.rm = TRUE),
    fl_yr1 = fl.2005,
    fl_yr2 = fl.2006,
    fl_yr3 = fl.2007,
    fl_yr4 = fl.2008,
    fl_yr5 = fl.2009,
    # Pre variables
    fl_pre_5cell = fl.2003 + A395 + A463,
    # Forest.pre = col314 - rowSums(cols 287:289)
    forest_pre = .[[314]] - rowSums(across(all_of(287:289)), na.rm = TRUE),
    pop_den_1km_pre  = A183,
    pop_den_5km_pre  = A186,
    pop_den_10km_pre = A184,
    dist_disturb_pre = A118,
    wave = "four") %>%
  filter(forest_pre > 450000, A346 == 0)

wave_2005 <- data %>%
  filter(A352 %in% c(0, 5)) %>%
  mutate(
    # 5-year post-PML sum + each year
    fl_5yr_postPML = rowSums(across(fl.2006:fl.2010), na.rm = TRUE),
    fl_yr1 = fl.2006,
    fl_yr2 = fl.2007,
    fl_yr3 = fl.2008,
    fl_yr4 = fl.2009,
    fl_yr5 = fl.2010,
    # Pre variables
    fl_pre_5cell = fl.2004 + A396 + A464,
    # Forest.pre = col314 - rowSums(cols 287:290)
    forest_pre = .[[314]] - rowSums(across(all_of(287:290)), na.rm = TRUE),
    pop_den_1km_pre  = A188,
    pop_den_5km_pre  = A191,
    pop_den_10km_pre = A189,
    dist_disturb_pre = A119,
    wave = "five") %>%
  filter(forest_pre > 450000, A346 == 0)

wave_2006 <- data %>%
  filter(A352 %in% c(0, 6)) %>%
  mutate(
    # 5-year post-PML sum + each year
    fl_5yr_postPML = rowSums(across(fl.2007:fl.2011), na.rm = TRUE),
    fl_yr1 = fl.2007,
    fl_yr2 = fl.2008,
    fl_yr3 = fl.2009,
    fl_yr4 = fl.2010,
    fl_yr5 = fl.2011,
    # Pre variables
    fl_pre_5cell = fl.2005 + A397 + A465,
    # Forest.pre = col314 - rowSums(cols 287:291)
    forest_pre = .[[314]] - rowSums(across(all_of(287:291)), na.rm = TRUE),
    pop_den_1km_pre  = A193,
    pop_den_5km_pre  = A196,
    pop_den_10km_pre = A194,
    dist_disturb_pre = A120,
    wave = "six") %>%
  filter(forest_pre > 450000, A346 == 0)

wave_2007 <- data %>%
  filter(A352 %in% c(0, 7)) %>%
  mutate(
    # 5-year post-PML sum + each year
    fl_5yr_postPML = rowSums(across(fl.2008:fl.2012), na.rm = TRUE),
    fl_yr1 = fl.2008,
    fl_yr2 = fl.2009,
    fl_yr3 = fl.2010,
    fl_yr4 = fl.2011,
    fl_yr5 = fl.2012,
    # Pre variables
    fl_pre_5cell = fl.2006 + A398 + A466,
    # Forest.pre = col314 - rowSums(cols 287:292)
    forest_pre = .[[314]] - rowSums(across(all_of(287:292)), na.rm = TRUE),
    pop_den_1km_pre  = A198,
    pop_den_5km_pre  = A201,
    pop_den_10km_pre = A199,
    dist_disturb_pre = A121,
    wave = "seven") %>%
  filter(forest_pre > 450000, A346 == 0)

# Combine the different yearly datasets into one.
data_flat <- rbind(wave_2002, wave_2003, wave_2004, wave_2005, wave_2006, wave_2007)
```

#### **Data Description**

The dataset used to reproduce the analysis in Buntaine et al. (2015) was constructed in GIS by overlaying several spatial datasets across a regular grid of 27,984 cells (~0.87 km² each) covering the Morona-Santiago province of Ecuador. Each grid cell represents the fundamental unit of observation, and raster and vector datasets covering the period 2001–2012 were extracted to the centroid of each cell to produce a tabular database. The raw dataset contains 27,984 observations with 395 variables. Each observation is identified with an `OBJECTID` and a `pointID`, geographic coordinates, and the relevant covariates in the study, encoded as `A100` to `A486` with variable definitions stored in associated metadata. 

This dataset was cleaned to produce a “flat” dataset where each row is a plot-wave combination. Waves (`A352`) to represent the years where land titling was implemented under PSUR. Wave 2 corresponds to communities titled in 2002, wave 3 to communities titled in 2003, and so on through wave 7. Untreated control plots (`A352 == 0`) appear in multiple waves, each time with covariates and outcomes aligned to each wave’s treatment year, allowing them to serve as counterfactuals. Each plot-wave combination has variables associated with the outcome (`fl.5yr.postPML`) or forest loss five years after wave’s treatment, pre-treatment covariates measured before the wave’s treatment, and an associated control plot. 

Pre-treatment covariates are constructed in two ways. Time-varying covariates, such as population density (`pop.den.1km.pre`), are measured annually and stored in successive columns, with each wave assigned the most recent pre-treatment value. Forest loss was calculated spatially and is a composite of three calculations: 1) forest loss in the plot itself in the year before treatment (e.g., `fl.2001`);  2) forest loss in the surrounding 3x3 neighborhood, and 3) forest loss in the surrounding 5x5 neighborhood. To produce `fl.pre`, forest loss was subtracted from total forest cover. Other variables such as distance to roads, distance to rivers, protected area status, were fixed in the dataset since they do not change year to year. 

Outcome variables were `PML` (Plan de Manejo para Legalización) and `PMI` (Plan de Manejo Integral). `PML` (`A352 == 2`)  was determined by plots that received land title without a community management plan in 2002 and `PMI` was determined by plots titled in 2003 or later (`A352 == 3`, etc.) that received a title and management plan. 

## Study Replication

#### Assumptions

**What assumptions must hold for the estimates to be causally valid?**

*Parallel Assumption*: Treatment and Control groups were moving in the same direction before the intervention began.

```{r}
# Create a line graph (PML) for the parallel trends assumption.

# Select the yearly deforestation of the treatment and control groups for PML and PMI
parallel <- data %>% 
  select(fl.2001, fl.2002, fl.2003, fl.2004, fl.2005, 
         fl.2006, fl.2007, fl.2008, fl.2009, fl.2010, fl.2011, 
         PML, PMI) %>%
  pivot_longer(cols = starts_with("fl."),
               names_to = "year",
               values_to = "deforestation") %>% 
  mutate(year = as.numeric(str_remove(year, "fl\\.")))

parallel_trends_PML <- parallel %>%
  group_by(year, PML) %>%
  summarise(
    mean_deforestation = mean(deforestation, na.rm = TRUE),
    .groups = "drop")

ggplot(parallel_trends_PML, 
       aes(x = year, y = mean_deforestation, color = factor(PML))) +
  geom_line() +
  geom_point(size = 3) +
  # Vertical line for the implement of treatment
  geom_vline(xintercept = 2002, 
             linetype = "dashed", 
             color = "gray30", 
             linewidth = 1) +
  annotate("label", 
           x = 2002, 
           y = 1250, 
           label = "PML implementation", 
           hjust = 0, 
           size = 2.5) +
  labs(
    title = "Yearly Deforestation Trends: PML vs non-PML areas",
    x = "Date",
    y = expression(paste("Deforestation (", m^2," per ", km^2, ")")),
    color = "PML") +
  theme_minimal() +
  scale_color_brewer(palette = "Set1", 
                     labels = c("0" = "Control Plot",
                                "1" = "Treatment Plot")) +
  theme(legend.title = element_blank())
```

**Assumption Interpretation**:

It appears that before treatment, the study areas do not follow the same trends. In addition, the authors only include pre-treatment data from 2001 and beyond; this does not provide enough data to determine whether the treatment and control groups followed parallel trends. Therefore, this implies that the parallel trends assumption is not met, and therefore, the control groups may not provide a good counterfactual for the treatment group. 


```{r}
# Create a line graph (PMI) for the parallel trends assumption. 
parallel_trends_PMI <- parallel %>%
  group_by(year, PMI) %>%
  summarise(
    mean_deforestation = mean(deforestation, na.rm = TRUE),
    .groups = "drop")

ggplot(parallel_trends_PMI, 
       aes(x = year, y = mean_deforestation, color = factor(PMI))) +
  geom_line() +
  geom_point(size = 3) +
  # Vertical line for the implement of treatment.
  geom_vline(xintercept = 2002, 
             linetype = "dashed", 
             color = "gray30", 
             linewidth = 1) +
  annotate("label", 
           x = 2002, 
           y = 1250, 
           label = "PMI implementation", 
           hjust = 0, 
           size = 2.5) +
  labs(
    title = "Yearly Deforestation Trends: PMI vs non-PMI areas",
    x = "Date",
    y = expression(paste("Deforestation (", m^2," per ", km^2, ")"))) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1", 
                     labels = c("0" = "Control Plot",
                                "1" = "Treatment Plot")) +
  theme(legend.title = element_blank())
```

## Difference in Difference 

```{r, results='hide'}
# Subset data.
data_PMLonly_flat <- subset(data_flat, PML == 0 | (PML == 1 & PMI == 0))
```

### Remaking Figure 5 From Original Study

```{r}
# Model 1 is year-on-year decomposition of covariates.
m1.PML1 <- lm(fl_yr1 ~ PML + 
                fl_pre_5cell + 
                forest_pre + 
                pop_den_5km_pre + 
                dist_disturb_pre + 
                A128 + A129 + A130 + A154 + A347 + A361 + A362, 
              data = data_PMLonly_flat)
summary(m1.PML1)

m1.PML2 <- lm(fl_yr2 ~ PML + 
                fl_pre_5cell + 
                forest_pre + 
                pop_den_5km_pre + 
                dist_disturb_pre + 
                A128 + A129 + A130 +  A154 + A347 + A361 + A362, 
              data = data_PMLonly_flat)
summary(m1.PML2)

m1.PML3 <- lm(fl_yr3 ~ PML + 
                fl_pre_5cell + 
                forest_pre + 
                pop_den_5km_pre + 
                dist_disturb_pre + 
                A128 + A129 + A130 + A154 + A347 + A361 + A362, 
              data = data_PMLonly_flat)
summary(m1.PML3)

m1.PML4 <- lm(fl_yr4 ~ PML + 
                fl_pre_5cell + 
                forest_pre + 
                pop_den_5km_pre + 
                dist_disturb_pre + 
                A128 + A129 + A130 + A154 + A347 + A361 + A362, 
              data = data_PMLonly_flat)
summary(m1.PML4)

m1.PML5 <- lm(fl_yr5 ~ PML + 
                fl_pre_5cell + 
                forest_pre + 
                pop_den_5km_pre + 
                dist_disturb_pre + 
                A128 + A129 + A130 + A154 + A347 + A361 + A362, 
              data = data_PMLonly_flat)
summary(m1.PML5)
```

```{r, results='hide'}
# Matching for PML data.
data_make <- make(data_PMLonly_flat, 
                  c(fl_5yr_postPML, fl_yr1, fl_yr2, fl_yr3, fl_yr4, fl_yr5, 
                    PML, fl_pre_5cell, forest_pre, pop_den_5km_pre, 
                    dist_disturb_pre, A128, A129, A130, A154, A347, A361, A362))

# Using the Mahlanobis matching method
out_PMLonly_flat <- matchit(PML ~ fl_pre_5cell + 
                              forest_pre + 
                              pop_den_5km_pre + 
                              dist_disturb_pre +
                              A128 + A129 + A130 + A154 + A347 + A361 + A362,
                            data = data_make,
                            method = "nearest", 
                            distance = "mahalanobis", 
                            discard = "none",
                            ratio = 1)

# Summary of covariate balance after matching
s_PML <- summary(out_PMLonly_flat, interactions = T, standardize = T)
s_sum_matched_PML <- as.data.frame(s_PML$sum.matched)

# Matched dataframe.
data_PMLonly_flat_matched <- match.data(out_PMLonly_flat)
```

```{r}
# Model 2 is year-on-year decomposition of no covariates and pre-matching.
m2.PML1 <- lm(fl_yr1 ~ PML, 
              weights = weights, data = data_PMLonly_flat_matched)
summary(m2.PML1)

m2.PML2 <- lm(fl_yr2 ~ PML, 
              weights = weights, data = data_PMLonly_flat_matched)
summary(m2.PML2)

m2.PML3 <- lm(fl_yr3 ~ PML, 
              weights = weights, data = data_PMLonly_flat_matched)
summary(m2.PML3)

m2.PML4 <- lm(fl_yr4 ~ PML, 
              weights = weights, data = data_PMLonly_flat_matched)
summary(m2.PML4)

m2.PML5 <- lm(fl_yr5 ~ PML, 
              weights = weights,data = data_PMLonly_flat_matched)
summary(m2.PML5)
```

```{r}
# Model 3 is year-on-year decomposition of covariates and pre-matching.
m3.PML1 <- lm(fl_yr1 ~ PML + 
                fl_pre_5cell + 
                forest_pre + 
                pop_den_5km_pre + 
                dist_disturb_pre + 
                A128 + A129 + A130 + A154 + A347 + A361 + A362, 
              weights = weights, data = data_PMLonly_flat_matched)
summary(m3.PML1)

m3.PML2 <- lm(fl_yr2 ~ PML + 
                fl_pre_5cell + 
                forest_pre + 
                pop_den_5km_pre + 
                dist_disturb_pre + 
                A128 + A129 + A130 + A154 + A347 + A361 + A362, 
              weights = weights, data = data_PMLonly_flat_matched)
summary(m3.PML2)

m3.PML3 <- lm(fl_yr3 ~ PML + 
                fl_pre_5cell + 
                forest_pre + 
                pop_den_5km_pre + 
                dist_disturb_pre + 
                A128 + A129 + A130 + A154 + A347 + A361 + A362, 
              weights = weights, data = data_PMLonly_flat_matched)
summary(m3.PML3)

m3.PML4 <- lm(fl_yr4 ~ PML + 
                fl_pre_5cell + 
                forest_pre + 
                pop_den_5km_pre + 
                dist_disturb_pre + 
                A128 + A129 + A130 + A154 + A347 + A361 + A362, 
              weights = weights, data = data_PMLonly_flat_matched)
summary(m3.PML4)

m3.PML5 <- lm(fl_yr5 ~ PML + 
                fl_pre_5cell + 
                forest_pre + 
                pop_den_5km_pre + 
                dist_disturb_pre + 
                A128 + A129 + A130 + A154 + A347 + A361 + A362, 
              weights = weights, data = data_PMLonly_flat_matched)
summary(m3.PML5)
```

```{r, include=FALSE}
# Year by year effects of PML.
year <- seq(1:5)

m1.coef <- c(m1.PML1$coef[2], 
             m1.PML2$coef[2], 
             m1.PML3$coef[2], 
             m1.PML4$coef[2], 
             m1.PML5$coef[2])
m1.se <- c(coef(summary(m1.PML1))[2,2], 
           coef(summary(m1.PML2))[2,2], 
           coef(summary(m1.PML3))[2,2], 
           coef(summary(m1.PML4))[2,2], 
           coef(summary(m1.PML5))[2,2])

m2.coef <- c(m2.PML1$coef[2], 
             m2.PML2$coef[2], 
             m2.PML3$coef[2], 
             m2.PML4$coef[2], 
             m2.PML5$coef[2])
m2.se <- c(coef(summary(m2.PML1))[2,2], 
           coef(summary(m2.PML2))[2,2], 
           coef(summary(m2.PML3))[2,2], 
           coef(summary(m2.PML4))[2,2], 
           coef(summary(m2.PML5))[2,2])

m3.coef <- c(m3.PML1$coef[2], 
             m3.PML2$coef[2], 
             m3.PML3$coef[2], 
             m3.PML4$coef[2], 
             m3.PML5$coef[2])
m3.se <- c(coef(summary(m3.PML1))[2,2], 
           coef(summary(m3.PML2))[2,2], 
           coef(summary(m3.PML3))[2,2], 
           coef(summary(m3.PML4))[2,2], 
           coef(summary(m3.PML5))[2,2])
```

Model 1 is a linear regression model using the outcome variables, forest loss (`fl_yr`) on the treatment, Land Legalization Plans (`PML`), and the different control variables, for each of the years between 2003 and 2007, using unmatched data. This is represented as model 1

Then our code matches data using the Mahalanobis method

Model 2 is a linear regression model using the outcome variable, forest loss (`fl_yr`) on the treatment, Land Legalization Plans (`PML`), with no control variables but using the weights from the matching method and the matched data.

Model 3 is a linear regression model using the outcome variable, forest loss (`fl_yr`) on the treatment,  Land Legalization Plans (`PML`), including the control variables and the weights from the matching method and the matched data.

These models above are used to recreate Figure 5.

```{r}
#| fig-width: 10
#| fig-height: 6

# Graphing Figure 5 with our results.
df_5 <- data.frame(
  year = rep(year, 3),
  coef = c(m1.coef, m2.coef, m3.coef),
  se   = c(m1.se,   m2.se,   m3.se),
  model = factor(rep(c("Model 1", "Model 2", "Model 3"),
                     each = length(year)))) %>%
  mutate(ymin = coef - 2 * se,
         ymax = coef + 2 * se)

ggplot(df_5, aes(x = year, y = coef, color = model, fill = model)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_ribbon(aes(ymin = ymin, ymax = ymax),
              alpha = 0.4, 
              color = NA, 
              show.legend = FALSE) +
  geom_line(linewidth = 1.5) +
  coord_cartesian(xlim = c(0.8, 5.2),
                  ylim = c(-600, 400)) +
  scale_fill_manual(
    values = c(
      "Model 1" = "grey60", 
      "Model 2" = "dodgerblue", 
      "Model 3" = "plum")) +
  scale_color_manual(
    values = c(
      "Model 1" = "black", 
      "Model 2" = "blue", 
      "Model 3" = "purple"),
    labels = c(
      "Model 1" = "Model 1: Covariates",
      "Model 2" = "Model 2: No Covariates, Pre-Matching",
      "Model 3" = "Model 3: Covariates, Pre-Matching")) +
  labs(
    x = "Year",
    y = expression(paste("Effect on Deforestation (", m^2," per ", km^2, ")")),
    title = "Annual Effects Following PML-Only Treatment ") +
  theme_classic(base_size = 14) + 
  theme(legend.title =  element_blank(),
        legend.position = "bottom")
```
### Remaking Figure 7 From Original Study

The next models use supplementary management plans (PMI) as the treatment.

```{r, results='hide'}
# Subset data.
data_PMI_flat <- subset(data_flat, PML == 0 | (PML == 1 & PMI == 1))
```

```{r}
# Model 1 is year-on-year decomposition of covariates and NO pre-matching.
m1.1 <- lm(fl_yr1 ~ PMI + 
             fl_pre_5cell + 
             forest_pre + 
             pop_den_5km_pre + 
             dist_disturb_pre + 
             A128 + A129 + A130 + A154 + A347 + A361 + A362, 
           data = data_PMI_flat)
summary(m1.1)

m1.2 <- lm(fl_yr2 ~ PMI + 
             fl_pre_5cell + 
             forest_pre + 
             pop_den_5km_pre + 
             dist_disturb_pre + 
             A128 + A129 + A130 +  A154 + A347 + A361 + A362, 
           data = data_PMI_flat)
summary(m1.2)

m1.3 <- lm(fl_yr3 ~ PMI + 
             fl_pre_5cell + 
             forest_pre + 
             pop_den_5km_pre + 
             dist_disturb_pre + 
             A128 + A129 + A130 + A154 + A347 + A361 + A362, 
           data = data_PMI_flat)
summary(m1.3)

m1.4 <- lm(fl_yr4 ~ PMI + 
             fl_pre_5cell + 
             forest_pre + 
             pop_den_5km_pre + 
             dist_disturb_pre + 
             A128 + A129 + A130 + A154 + A347 + A361 + A362, 
           data = data_PMI_flat)
summary(m1.4)

m1.5 <- lm(fl_yr5 ~ PMI + 
             fl_pre_5cell + 
             forest_pre + 
             pop_den_5km_pre + 
             dist_disturb_pre + 
             A128 + A129 + A130 + A154 + A347 + A361 + A362, 
           data = data_PMI_flat)
summary(m1.5)
```

```{r, results='hide'}
# Matching for PMI data.
data_PMI_flat <- subset(data_flat, PML == 0 | (PML == 1 & PMI == 1))

data_make_2 <- make(data_PMI_flat,
                    c(fl_5yr_postPML, fl_yr1, fl_yr2, fl_yr3, fl_yr4, fl_yr5, 
                      PMI, fl_pre_5cell, forest_pre, pop_den_5km_pre, 
                      dist_disturb_pre, A128, A129, A130, A154, A347, A361, A362))

# Using the Mahlanobis matching method
out_PMI_flat <- matchit(PMI ~ fl_pre_5cell + 
                          forest_pre + 
                          pop_den_5km_pre + 
                          dist_disturb_pre + 
                          A128 + A129 + A130 + A154 + A347 + A361 + A362,
                        data = data_make_2,
                        method = "nearest",
                        distance = "mahalanobis",
                        discard = "none", 
                        ratio = 1)

# Summary of covariate balance after matching
s_PMI <- summary(out_PMI_flat, interactions = T, standardize = T)
s_sum_matched_PMI <- as.data.frame(s_PMI$sum.matched)

# Matched data frame.
data_PMI_flat_matched <- match.data(out_PMI_flat)
```

```{r}
# Model 2 is year-on-year decomposition of no covariates and pre-matching.
m2.1 <- lm(fl_yr1 ~ PMI, 
           weights = weights, data = data_PMI_flat_matched)
summary(m2.1)

m2.2 <- lm(fl_yr2 ~ PMI, 
           weights = weights, data = data_PMI_flat_matched)
summary(m2.2)

m2.3 <- lm(fl_yr3 ~ PMI, 
           weights = weights, data = data_PMI_flat_matched)
summary(m2.3)

m2.4 <- lm(fl_yr4 ~ PMI, 
           weights = weights, data = data_PMI_flat_matched)
summary(m2.4)

m2.5 <- lm(fl_yr5 ~ PMI, 
           weights = weights, data = data_PMI_flat_matched)
summary(m2.5)
```

```{r}
# Model 3 is year-on-year decomposition of covariates and pre-matching.
m3.1 <- lm(fl_yr1 ~ PMI + 
             fl_pre_5cell + 
             forest_pre + 
             pop_den_5km_pre + 
             dist_disturb_pre + 
             A128 + A129 + A130 +  A154 + A347 + A361 + A362, 
           weights = weights, data = data_PMI_flat_matched)
summary(m3.1)

m3.2 <- lm(fl_yr2 ~ PMI + 
             fl_pre_5cell + 
             forest_pre + 
             pop_den_5km_pre + 
             dist_disturb_pre + 
             A128 + A129 + A130 +  A154 + A347 + A361 + A362, 
           weights = weights, data = data_PMI_flat_matched)
summary(m3.2)

m3.3 <- lm(fl_yr3 ~ PMI + 
             fl_pre_5cell + 
             forest_pre + 
             pop_den_5km_pre + 
             dist_disturb_pre + 
             A128 + A129 + A130 +  A154 + A347 + A361 + A362, 
           weights = weights, data = data_PMI_flat_matched)
summary(m3.3)

m3.4 <- lm(fl_yr4 ~ PMI + 
             fl_pre_5cell + 
             forest_pre + 
             pop_den_5km_pre + 
             dist_disturb_pre + 
             A128 + A129 + A130 +  A154 + A347 + A361 + A362, 
           weights = weights, data = data_PMI_flat_matched)
summary(m3.4)

m3.5 <- lm(fl_yr5 ~ PMI + 
             fl_pre_5cell + 
             forest_pre + 
             pop_den_5km_pre + 
             dist_disturb_pre + 
             A128 + A129 + A130 + A154 + A347 + A361 + A362, 
           weights = weights, data = data_PMI_flat_matched)
summary(m3.5)
```

```{r, include=FALSE}
# Year by year effects of PMI.
year <- seq(1:5)
m1.coef <- c(m1.1$coef[2], 
             m1.2$coef[2], 
             m1.3$coef[2], 
             m1.4$coef[2], 
             m1.5$coef[2])
m1.se <- c(coef(summary(m1.1))[2,2], 
           coef(summary(m1.2))[2,2], 
           coef(summary(m1.3))[2,2], 
           coef(summary(m1.4))[2,2], 
           coef(summary(m1.5))[2,2])

m2.coef <- c(m2.1$coef[2], 
             m2.2$coef[2], 
             m2.3$coef[2], 
             m2.4$coef[2], 
             m2.5$coef[2])
m2.se <- c(coef(summary(m2.1))[2,2], 
           coef(summary(m2.2))[2,2], 
           coef(summary(m2.3))[2,2], 
           coef(summary(m2.4))[2,2], 
           coef(summary(m2.5))[2,2])

m3.coef <- c(m3.1$coef[2], 
             m3.2$coef[2], 
             m3.3$coef[2], 
             m3.4$coef[2], 
             m3.5$coef[2])
m3.se <- c(coef(summary(m3.1))[2,2], 
           coef(summary(m3.2))[2,2], 
           coef(summary(m3.3))[2,2], 
           coef(summary(m3.4))[2,2], 
           coef(summary(m3.5))[2,2])
```

Model 1 is a linear regression model using the outcome variables, forest loss (`fl_yr`) on the treatment, supplementary management plans (`PMI`), and the different control variables, for each of the years between 2003 and 2007, using unmatched data. This is represented as model 1

Then our code matches data using the Mahalanobis method

Model 2 is a linear regression model using the outcome variable, forest loss (`fl_yr`) on the treatment, supplementary management plans (`PMI`), with no control variables but using the weights from the matching method and the matched data.

Model 3 is a linear regression model using the outcome variable, forest loss (`fl_yr`) on the treatment, supplementary management plans (`PMI`), including the control variables and the weights from the matching method and the matched data.

These models above are used to recreate Figure 7.

```{r}
#| fig-width: 10
#| fig-height: 6

# Creating a dataframe of PMI model coefficients.
df_7 <- data.frame(
  year  = rep(year, 3),
  coef  = c(m1.coef, m2.coef, m3.coef),
  se    = c(m1.se,   m2.se,   m3.se),
  model = factor(rep(c("Model 1","Model 2","Model 3"),
                     each = length(year)))) %>%
  mutate(ymin = coef - 2 * se,
         ymax = coef + 2 * se)

# Plotting Figure 7.
ggplot(df_7, aes(x = year, y = coef)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = model),
              alpha = 0.4, 
              color = NA, 
              show.legend = FALSE) +
  # Coefficient lines.
  geom_line(aes(color = model), linewidth = 1.8) +
  coord_cartesian(xlim = c(0.8, 5.2),
                  ylim = c(-500, 400)) +
  scale_fill_manual(
    values = c(
      "Model 1" = "grey60", 
      "Model 2" = "dodgerblue", 
      "Model 3" = "plum")) +
  scale_color_manual(
    values = c(
      "Model 1" = "black", 
      "Model 2" = "blue", 
      "Model 3" = "purple"),
    labels = c(
      "Model 1" = "Model 1: Covariates",
      "Model 2" = "Model 2: No Covariates, Pre-Matching",
      "Model 3" = "Model 3: Covariates, Pre-Matching")) +
  labs(
    x = "Year",
    y = expression(paste("Effect on Deforestation (", m^2, " per ", km^2, ")")),
    title = "Annual Effects Following Titling and PMI Treatment ") +
  theme_classic(base_size = 14) + 
  theme(legend.title =  element_blank(),
        legend.position = "bottom")
```

#### Annotated Replication

**What is the causal identification approach? (e.g., DiD, RDD, IV, matching)**
  
The causal identification approach is Difference in Difference

The authors used a genetic matching method for their study, due to long run times from the original code. As a substitute, we used the Mahalanobis matching method as a way to still implement a matching method and compare how the results from our replication differ from the real study results. Since the Mahalanobis method uses nearest neighbor based on a distance metric there may still be remnants of bias, as this method does not optimize balance like genetic matching does. Mahalanobis is an okay alternative for us since our sample size is large with covariates that are already fairly balanced.

```{r}
head(s_sum_matched_PML)
head(s_sum_matched_PMI)
```


## Evaluation

#### Closing

**Causal identification**: 

The identification strategy of this study is credible but has some serious limitations, which the authors largely acknowledge. Several assumptions must hold in order for the estimates to be causal.
  
First, there shouldn’t be unobserved variables simultaneously affecting which grid cells get assigned to the treatment group and forest cover. Failing to account  for these kinds of variables could compromise accuracy of the genetic matching conducted in this study. It would mean the control and treatment groups would only be balanced on observed variables and exclude this confounding variable. 
  
Second, the parallel trends assumptions must be true. This means that in the absence of treatment (the implementation of the land titling program) treated and controlled grid cells would have the same trend in forest cover over time. 
  
Lastly, there should not be spillover effects between control and treatment grid cells. The impacts of the land titling program on the treatment group should not impact deforestation in the control group. 

**Statistical assumptions**:

Several key assumptions are defended in this study, some of which are better defended than others. 
The authors try to defend the parallel trends assumption, but it is probably their weakest assumption. They only use one year of pre-treatment data, meaning there isn't a lot of evidence that the treated and controlled grid cells were following the same deforestation rates before the land titling program. They use a pre-treatment deforestation covariate for the genetic matching process in order to ensure treated and control grid cells had similar deforestation rates before the program. This is a great way to strengthen the parallel trends assumption, but it cannot replace the robustness of using more pre-treatment data.

The authors also assume there aren't any unobserved confounding variables simultaneously affecting which groups got treated and forest deforestation. We believe the authors did a great job of matching on observables such as pre-treatment forest loss, distance to roads, slope, etc. However, an unobservable that should probably be accounted for is quality of governance for the community. Communities had to have a functioning governance system in order for them to be selected into the land titling program in the first place and quality governance is also needed to effectively manage deforestation rates. This means this unobserved variable is a potential confound for the study. While we think this study would be stronger if they accounted for this unobserved variable, We do think they accounted for most of the strongest observables and we find the matching strategy convincing. 

Lastly, the spillover effect is mentioned by the authors but not tested. The authors acknowledge it is possible that colonists displaced from the titled area may move into adjacent untitled areas and cause deforestation there. This could make the impact of the land titling program artificially large. Interestingly, however, despite this potential spill over effect, the study showed little difference between titled and untitled lands. This may serve as an unofficial test of the spillover effect and indicate there is no spillover effect, however, an official test would have made this study more robust. 

**Sampling & external validity**: 

Communal and Indigenous areas in the heavily forested province of Morona-Santiago, Ecuador are included in this study. The treated satellite grid cells in this study come from land within the 52 communities that received title through the land titling program.
  
The results can be generalized to Indigenous communities in remote and heavily forested regions of Latin America that face colonization pressure, have limited commercial agriculture opportunities, and receive compensation through conservation programs. Also, these results are specific to collective land titles, deforestation under an individual private title might behave differently. Lastly, this study consisted of 5 years of observations so its results could only apply to programs that have a similar short run. We cannot extrapolate the results to long-term land titling programs. 

**Measurement**: 
  
The authors measured deforestation using satellite remote sensing data that uses 30-meter satellite pixels that were also aggregated by the authors to calculate deforestation within the five years after the implementation of treatment (PML and PMI). This can fail to capture small scale degradation, which would impact results in the way that there would appear to be less deforestation than there really is. Therefore, causing us to question whether the outcome variable was measured accurately. The outcome variable is measured without systematic bias since the land titling does not influence the independent data collection of deforestation.

The authors used spatial data to determine the boundaries of communities that were titled with PML or PMI. In areas where spatial data were missing, the authors estimated the boundaries by referencing settlement locations. Systematic bias is unlikely in the measurement of treatment variables, as the assignment of PML and PMI was made by officials rather than the researchers.


**Other limitations**: 

There might be some precision concerns with this study for not including a covariate for rainfall and cloud cover when matching treatment and control grid cells. Rainfall and cloud cover directly impact forest cover and not accounting for them in this study increases standard errors. 
  
Also, this study only reported the treated cell group mean, the pre-matching control cell group mean, and post-matching control cell group mean after conducting genetic matching. Visually, it seems that the post-matching control cell group mean got much closer to the pre-matching control cell group mean (Buntaine et al., 2015, Table B1). This matching would be more credible, however, if the standard mean difference (SMD) was reported before and after matching so we can account for variation when assessing balance between treatment and control groups. 


#### References

Buntaine, Mark; Hamilton, Stuart; Millones, Marco, 2015, "BHM_GEC_replication.R", Replication Data for: Titling community land to prevent deforestation: An evaluation of a best-case program in Morona-Santiago, Ecuador, [https://doi.org/10.7910/DVN/GT6EJJ/GPFQWQ](https://doi.org/10.7910/DVN/GT6EJJ/GPFQWQ), Harvard Dataverse, V1

Buntaine, Mark T., et al. “Titling Community Land to Prevent Deforestation: An Evaluation of a Best-Case Program in Morona-Santiago, Ecuador.” Global Environmental Change, vol. 33, July 2015, pp. 32–43, [https://doi.org/10.1016/j.gloenvcha.2015.04.001](https://doi.org/10.1016/j.gloenvcha.2015.04.001). Accessed 2 Apr. 2022.

Buntaine, Mark; Hamilton, Stuart; Millones, Marco, 2015, "Replication Data for: Titling community land to prevent deforestation: An evaluation of a best-case program in Morona-Santiago, Ecuador", [https://doi.org/10.7910/DVN/GT6EJJ](https://doi.org/10.7910/DVN/GT6EJJ), Harvard Dataverse, V1, UNF:6:LTM4EGL0a0yLM4O0n1OUeQ== [fileUNF]

