---
title: "final"
format: html
author: "Jaslyn, Isabella, Richie"
---

```{r}
library(tidyverse)
library(dplyr)
```

## Data

```{r}
data <- read_csv(here::here("data", "BHM_sample20.csv"))

##Treatment variables
data$PML <- ifelse(data$A352==0,0,1)
data$PMI <- ifelse(data$A352>=3,1,0) #Note: all PSUR intervention had PMI in 2003 and after
names(data)[287:298] <- c("fl.2001","fl.2002","fl.2003","fl.2004","fl.2005","fl.2006","fl.2007","fl.2008","fl.2009","fl.2010","fl.2011","fl.2012")
data$toPeru.km <- data$A486/1000

# #This function remakes the data frame with only the specified columns & NAs removed:
# make <- function(data,names) {
#   datasub <- as.data.frame(data)
#   sub = substitute(names)
#   names <- as.character(sub)
#   data.make <- subset(datasub, select=names(datasub) %in% names)
#   data.make <<- na.omit(data.make)
#   data.make <- na.omit(data.make)
#   print(c("ob =",nrow(data.make)),quote=F)}
# #Example> make(c(monit2other,sa1all))

make <- function(data, names) {

  # Capture unquoted variable names
  vars <- as.character(substitute(names))[-1]

  # Subset and remove NA rows
  data.make <- data[, vars, drop = FALSE]
  data.make <- na.omit(data.make)

  # Print number of observations
  cat("ob =", nrow(data.make), "\n")

  return(data.make)
}

```

```{r}
# create a line graph (PML) for the parallel trends assumption

parallel <- data %>% 
  select(fl.2001, fl.2002, fl.2003, fl.2004, fl.2005, fl.2006, fl.2007, fl.2008, fl.2009, fl.2010, fl.2011, PML, PMI) %>%
  pivot_longer(
    cols = starts_with("fl."),
    names_to = "year",
    values_to = "deforestation") %>% 
  mutate(year = as.numeric(str_remove(year, "fl\\.")))

parallel_trends_PML <- parallel %>%
  group_by(year, PML) %>%
  summarise(
    mean_deforestation = mean(deforestation, na.rm = TRUE),
    .groups = "drop")

ggplot(parallel_trends_PML, aes(x = year, y = mean_deforestation, color = factor(PML))) +
  geom_line() +
  geom_point(size = 3) +
  # vertical line for the implement of treatment
  geom_vline(xintercept = 2002, linetype = "dashed", color = "gray30", size = 1) +
  annotate("label", x = 2002, y = 1250, label = "PML implementation", hjust = 0, size = 2.5) +
  labs(
    title = "Yearly Deforestation Trends: PML vs non-PML areas",
    x = "Date",
    y = "Deforestation (m^2 per km^2)",
    color = "PML") +
  theme_minimal() +
  scale_color_brewer(palette = "Set1")
```
```{r}
# create a line graph (PMI) for the parallel trends assumption 

parallel_trends_PMI <- parallel %>%
  group_by(year, PMI) %>%
  summarise(
    mean_deforestation = mean(deforestation, na.rm = TRUE),
    .groups = "drop")

ggplot(parallel_trends_PMI, aes(x = year, y = mean_deforestation, color = factor(PMI))) +
  geom_line() +
  geom_point(size = 3) +
  # vertical line for the implement of treatment
  geom_vline(xintercept = 2002, linetype = "dashed", color = "gray30", size = 1) +
  annotate("label", x = 2002, y = 1250, label = "PML implementation", hjust = 0, size = 2.5) +
  labs(
    title = "Yearly Deforestation Trends: PMI vs non-PMI areas",
    x = "Date",
    y = "Deforestation (m^2 per km^2)",
    color = "PMI") +
  theme_minimal() +
  scale_color_brewer(palette = "Set1")

```


```{r}
# could make a function to run through all the waves... 

wave_2002 <- data %>%
  # keep A352 == 0 or 2
  filter(A352 %in% c(0, 2)) %>%
  mutate(
    # post PML totals + each year
    fl_5yr_postPML = fl.2003 + fl.2004 + fl.2005 + fl.2006 + fl.2007,
    fl_yr1 = fl.2003,
    fl_yr2 = fl.2004,
    fl_yr3 = fl.2005,
    fl_yr4 = fl.2006,
    fl_yr5 = fl.2007,

    # pre vars
    fl_pre_5cell = fl.2001 + A393 + A461,

    # same as wave.2002[,314] - wave.2002[,287]
    forest_pre = .[[314]] - .[[287]],

    pop_den_1km_pre  = A173,
    pop_den_5km_pre  = A176,
    pop_den_10km_pre = A174,
    dist_disturb_pre = A116,

    wave = "two"
  ) %>%
  # final filters
  filter(forest_pre > 450000, A346 == 0)

wave_2003 <- data %>%
  filter(A352 %in% c(0, 3)) %>%
  mutate(
    # 5-year post-PML sum + each year
    fl_5yr_postPML = fl.2004 + fl.2005 + fl.2006 + fl.2007 + fl.2008,
    fl_yr1 = fl.2004,
    fl_yr2 = fl.2005,
    fl_yr3 = fl.2006,
    fl_yr4 = fl.2007,
    fl_yr5 = fl.2008,

    # pre variables
    fl_pre_5cell = fl.2002 + A394 + A462,

    # forest.pre = col314 - rowSums(cols 287:288)
    forest_pre = .[[314]] - rowSums(across(all_of(287:288)), na.rm = TRUE),

    pop_den_1km_pre  = A178,
    pop_den_5km_pre  = A181,
    pop_den_10km_pre = A179,
    dist_disturb_pre = A117,

    wave = "three"
  ) %>%
  filter(forest_pre > 450000, A346 == 0)

wave_2004 <- data %>%
  filter(A352 == 0) %>%
  mutate(
    # 5-year post-PML sum + each year
    fl_5yr_postPML = rowSums(across(fl.2005:fl.2009), na.rm = TRUE),
    fl_yr1 = fl.2005,
    fl_yr2 = fl.2006,
    fl_yr3 = fl.2007,
    fl_yr4 = fl.2008,
    fl_yr5 = fl.2009,

    # pre variables
    fl_pre_5cell = fl.2003 + A395 + A463,

    # forest.pre = col314 - rowSums(cols 287:289)
    forest_pre = .[[314]] - rowSums(across(all_of(287:289)), na.rm = TRUE),

    pop_den_1km_pre  = A183,
    pop_den_5km_pre  = A186,
    pop_den_10km_pre = A184,
    dist_disturb_pre = A118,

    wave = "four"
  ) %>%
  filter(forest_pre > 450000, A346 == 0)

wave_2005 <- data %>%
  filter(A352 %in% c(0, 5)) %>%
  mutate(
    # 5-year post-PML sum + each year
    fl_5yr_postPML = rowSums(across(fl.2006:fl.2010), na.rm = TRUE),
    fl_yr1 = fl.2006,
    fl_yr2 = fl.2007,
    fl_yr3 = fl.2008,
    fl_yr4 = fl.2009,
    fl_yr5 = fl.2010,

    # pre variables
    fl_pre_5cell = fl.2004 + A396 + A464,

    # forest.pre = col314 - rowSums(cols 287:290)
    forest_pre = .[[314]] - rowSums(across(all_of(287:290)), na.rm = TRUE),

    pop_den_1km_pre  = A188,
    pop_den_5km_pre  = A191,
    pop_den_10km_pre = A189,
    dist_disturb_pre = A119,

    wave = "five"
  ) %>%
  filter(forest_pre > 450000, A346 == 0)

wave_2006 <- data %>%
  filter(A352 %in% c(0, 6)) %>%
  mutate(
    # 5-year post-PML sum + each year
    fl_5yr_postPML = rowSums(across(fl.2007:fl.2011), na.rm = TRUE),
    fl_yr1 = fl.2007,
    fl_yr2 = fl.2008,
    fl_yr3 = fl.2009,
    fl_yr4 = fl.2010,
    fl_yr5 = fl.2011,

    # pre variables
    fl_pre_5cell = fl.2005 + A397 + A465,

    # forest.pre = col314 - rowSums(cols 287:291)
    forest_pre = .[[314]] - rowSums(across(all_of(287:291)), na.rm = TRUE),

    pop_den_1km_pre  = A193,
    pop_den_5km_pre  = A196,
    pop_den_10km_pre = A194,
    dist_disturb_pre = A120,

    wave = "six"
  ) %>%
  filter(forest_pre > 450000, A346 == 0)

wave_2007 <- data %>%
  filter(A352 %in% c(0, 7)) %>%
  mutate(
    # 5-year post-PML sum + each year
    fl_5yr_postPML = rowSums(across(fl.2008:fl.2012), na.rm = TRUE),
    fl_yr1 = fl.2008,
    fl_yr2 = fl.2009,
    fl_yr3 = fl.2010,
    fl_yr4 = fl.2011,
    fl_yr5 = fl.2012,

    # pre variables
    fl_pre_5cell = fl.2006 + A398 + A466,

    # forest.pre = col314 - rowSums(cols 287:292)
    forest_pre = .[[314]] - rowSums(across(all_of(287:292)), na.rm = TRUE),

    pop_den_1km_pre  = A198,
    pop_den_5km_pre  = A201,
    pop_den_10km_pre = A199,
    dist_disturb_pre = A121,

    wave = "seven"
  ) %>%
  filter(forest_pre > 450000, A346 == 0)

data_flat <- rbind(wave_2002, wave_2003, wave_2004, wave_2005, wave_2006, wave_2007)
```


1. Data Description
After the code block(s) that read in and clean the data, add some notes covering:

What does each row represent? What is the unit of observation?
What are the key outcome, treatment, and control variables?
Any notable data cleaning decisions (dropped observations, constructed variables, etc.)
Sample size, time period, and geographic scope

## Study Replication

```{r}
### figure 5 recreation

data_PMLonly_flat <- subset(data_flat, PML==0 | (PML==1 & PMI==0))

#Model 1 is year-on-year decomposition of Model (a) in Figure 4
m1.PML1 <- lm(fl_yr1 ~ PML + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, data=data_PMLonly_flat)
summary(m1.PML1)
m1.PML2 <- lm(fl_yr2 ~ PML + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, data=data_PMLonly_flat)
summary(m1.PML2)
m1.PML3 <- lm(fl_yr3 ~ PML + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, data=data_PMLonly_flat)
summary(m1.PML3)
m1.PML4 <- lm(fl_yr4 ~ PML + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, data=data_PMLonly_flat)
summary(m1.PML4)
m1.PML5 <- lm(fl_yr5 ~ PML + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, data=data_PMLonly_flat)
summary(m1.PML5)

# running a different matching method

library(MatchIt)

data_make <- make(data_PMLonly_flat, 
                  c(fl_5yr_postPML, fl_yr1, fl_yr2, fl_yr3, fl_yr4, fl_yr5, PML, fl_pre_5cell, forest_pre, pop_den_5km_pre, dist_disturb_pre, A128, A129, A130, A154, A347, A361, A362))

out_PMLonly_flat <- matchit(PML ~ fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre +
                A128 + A129 + A130 + A154 + A347 + A361 + A362,
              data = data_make,
              method = "nearest", distance = "mahalanobis", discard = "none")
s <- summary(out_PMLonly_flat,interactions=T,standardize=T)
# s_nn <- as.data.frame(s$nn)
# s_sum_all <- as.data.frame(s$sum.all)
# THIS TABLE WILL TELL US HOW WELL THE MATCHING MATCHED THE COVARIATES
s_sum_matched <- as.data.frame(s$sum.matched)

data_PMLonly_flat_matched <- match.data(out_PMLonly_flat)

# Model 2 is year-on-year decomposition of Model (b) in Figure 4 ### THISIS USING MATCHING DATA!!!
m2.PML1 <- lm(fl_yr1 ~ PML, weights = weights, data = data_PMLonly_flat_matched)
summary(m2.PML1)
m2.PML2 <- lm(fl_yr2 ~ PML, weights = weights, data = data_PMLonly_flat_matched)
summary(m2.PML2)
m2.PML3 <- lm(fl_yr3 ~ PML, weights = weights, data = data_PMLonly_flat_matched)
summary(m2.PML3)
m2.PML4 <- lm(fl_yr4 ~ PML, weights = weights, data = data_PMLonly_flat_matched)
summary(m2.PML4)
m2.PML5 <- lm(fl_yr5 ~ PML, weights = weights, data = data_PMLonly_flat_matched)
summary(m2.PML5)

#Model 3 is year-on-year decomposition of Model (c) in Figure 6 #### THIS IS USING MATCHING DATA!!
m3.PML1 <- lm(fl_yr1 ~ PML + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, weights = weights, data = data_PMLonly_flat_matched)
summary(m3.PML1)
m3.PML2 <- lm(fl_yr2 ~ PML + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, weights = weights, data = data_PMLonly_flat_matched)
summary(m3.PML2)
m3.PML3 <- lm(fl_yr3 ~ PML + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, weights = weights, data = data_PMLonly_flat_matched)
summary(m3.PML3)
m3.PML4 <- lm(fl_yr4 ~ PML + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, weights = weights, data = data_PMLonly_flat_matched)
summary(m3.PML4)
m3.PML5 <- lm(fl_yr5 ~ PML + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, weights = weights, data = data_PMLonly_flat_matched)
summary(m3.PML5)

##Year by year effects of PML
year <- seq(1:5)
m1.coef <- c(m1.PML1$coef[2],m1.PML2$coef[2],m1.PML3$coef[2],m1.PML4$coef[2],m1.PML5$coef[2])
m1.se <- c(coef(summary(m1.PML1))[2,2],coef(summary(m1.PML2))[2,2],coef(summary(m1.PML3))[2,2],coef(summary(m1.PML4))[2,2],coef(summary(m1.PML5))[2,2])
m2.coef <- c(m2.PML1$coef[2],m2.PML2$coef[2],m2.PML3$coef[2],m2.PML4$coef[2],m2.PML5$coef[2])
m2.se <- c(coef(summary(m2.PML1))[2,2],coef(summary(m2.PML2))[2,2],coef(summary(m2.PML3))[2,2],coef(summary(m2.PML4))[2,2],coef(summary(m2.PML5))[2,2])
m3.coef <- c(m3.PML1$coef[2],m3.PML2$coef[2],m3.PML3$coef[2],m3.PML4$coef[2],m3.PML5$coef[2])
m3.se <- c(coef(summary(m3.PML1))[2,2],coef(summary(m3.PML2))[2,2],coef(summary(m3.PML3))[2,2],coef(summary(m3.PML4))[2,2],coef(summary(m3.PML5))[2,2])

# par(mar = c(4.1, 5.1, 1.1, 1.1))
# plot(1,type="n",xlim=c(0.8,5.2),ylim=c(-600,400), ylab=expression(paste("Effect on Deforestation (",m^{2} ," per " ,km^{2},")")),xlab="Year", cex.lab=1.2, cex.axis=1.2)
# abline(h=0, lty=2)
# polygon(x=c(year[1:5],year[5:1]),y=c(m1.coef+2*m1.se,m1.coef[5:1]-2*m1.se[5:1]),col=rgb(.6,.6,.6,0.5), border=NA)
# polygon(x=c(year[1:5],year[5:1]),y=c(m2.coef+2*m2.se,m2.coef[5:1]-2*m2.se[5:1]),col=rgb(0, 0, 0.8,0.5), border=NA)
# polygon(x=c(year[1:5],year[5:1]),y=c(m3.coef+2*m3.se,m3.coef[5:1]-2*m3.se[5:1]),col=rgb(0, 0, 1,0.5), border=NA)
# lines(year,m1.coef,type="l",col="black",lwd=5)
# lines(year,m2.coef,type="l",col="blue",lwd=5)
# lines(year,m3.coef,type="l",col="blue",lwd=5)

```

```{r}
# remake figure 5
df <- tibble(
  year = year,
  coef = m1.coef,
  se   = m1.se
) %>%
  mutate(
    ymin = coef - 2 * se,
    ymax = coef + 2 * se
  )

ggplot(df, aes(x = year, y = coef)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_ribbon(aes(ymin = ymin, ymax = ymax),
              fill = "grey60", alpha = 0.5) +
  geom_line(color = "black", linewidth = 1.6) +
  coord_cartesian(xlim = c(0.8, 5.2), ylim = c(-600, 400)) +
  labs(
    x = "Year",
    y = expression(paste("Effect on Deforestation (", m^2, " per ", km^2, ")"))
  ) +
  theme_classic(base_size = 14) +
  theme(
    axis.title = element_text(size = 14),
    axis.text  = element_text(size = 12)
  )

df_5 <- data.frame(
  year = rep(year, 3),
  coef = c(m1.coef, m2.coef, m3.coef),
  se   = c(m1.se,   m2.se,   m3.se),
  model = factor(rep(c("Model 1", "Model 2", "Model 3"),
                     each = length(year)))
) %>%
  mutate(
    ymin = coef - 2 * se,
    ymax = coef + 2 * se
  )

ggplot(df_5, aes(x = year, y = coef, color = model, fill = model)) +

  geom_hline(yintercept = 0, linetype = 2) +

  geom_ribbon(aes(ymin = ymin, ymax = ymax),
              alpha = 0.4, color = NA) +

  geom_line(linewidth = 1.5) +

  coord_cartesian(xlim = c(0.8, 5.2),
                  ylim = c(-600, 400)) +

  scale_color_manual(values = c("black", "blue", "blue")) +
  scale_fill_manual(values = c("grey60", "darkblue", "blue")) +

  labs(
    x = "Year",
    y = expression(paste("Effect on Deforestation (", m^2,
                         " per ", km^2, ")"))
  ) +

  theme_classic(base_size = 14)

```

```{r}
### recreating figure 6

data_PMI_flat <- subset(data_flat, PML==0 | (PML==1 & PMI==1))

data_make_2 <- make(data_PMI_flat,
                    c(fl_5yr_postPML, fl_yr1, fl_yr2, fl_yr3, fl_yr4, fl_yr5, PMI, fl_pre_5cell, forest_pre, pop_den_5km_pre, dist_disturb_pre, A128, A129, A130, A154, A347, A361, A362))

out_PMI_flat <- matchit(
  PMI ~ fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre +
    A128 + A129 + A130 + A154 + A347 + A361 + A362,
  data = data_make_2,
  method = "nearest",
  distance = "mahalanobis",
  discard = "none",   # keep this the same as your genetic spec
  ratio = 1              # 1:1 matching (default)
)
summary(out_PMI_flat, interactions = TRUE, standardize = TRUE)

data_PMI_flat_matched <- match.data(out_PMI_flat)

###Figure 7

#Model 1 is year-on-year decomposition of Model (a) in Figure 6
m1.1 <- lm(fl_yr1 ~ PMI + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, data = data_PMI_flat)
summary(m1.1)
m1.2 <- lm(fl_yr2 ~ PMI + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, data = data_PMI_flat)
summary(m1.2)
m1.3 <- lm(fl_yr3 ~ PMI + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, data = data_PMI_flat)
summary(m1.3)
m1.4 <- lm(fl_yr4 ~ PMI + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, data = data_PMI_flat)
summary(m1.4)
m1.5 <- lm(fl_yr5 ~ PMI + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, data = data_PMI_flat)
summary(m1.5)

#Model 2 is year-on-year decomposition of Model (b) in Figure 6
m2.1 <- lm(fl_yr1 ~ PMI, weights = weights, data = data_PMI_flat_matched)
summary(m2.1)
m2.2 <- lm(fl_yr2 ~ PMI, weights = weights, data = data_PMI_flat_matched)
summary(m2.2)
m2.3 <- lm(fl_yr3 ~ PMI, weights = weights, data = data_PMI_flat_matched)
summary(m2.3)
m2.4 <- lm(fl_yr4 ~ PMI, weights = weights, data = data_PMI_flat_matched)
summary(m2.4)
m2.5 <- lm(fl_yr5 ~ PMI, weights = weights, data = data_PMI_flat_matched)
summary(m2.5)

#Model 3 is year-on-year decomposition of Model (c) in Figure 6
m3.1 <- lm(fl_yr1 ~ PMI + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, weights = weights, data = data_PMI_flat_matched)
summary(m3.1)
m3.2 <- lm(fl_yr2 ~ PMI + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, weights = weights, data = data_PMI_flat_matched)
summary(m3.2)
m3.3 <- lm(fl_yr3 ~ PMI + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, weights = weights, data = data_PMI_flat_matched)
summary(m3.3)
m3.4 <- lm(fl_yr4 ~ PMI + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, weights = weights, data = data_PMI_flat_matched)
summary(m3.4)
m3.5 <- lm(fl_yr5 ~ PMI + fl_pre_5cell + forest_pre + pop_den_5km_pre + dist_disturb_pre + A128 + A129 + A130 + A154 + A347 + A361 + A362, weights = weights, data = data_PMI_flat_matched)
summary(m3.5)

##Year by year effects of PMI
year <- seq(1:5)
m1.coef <- c(m1.1$coef[2],m1.2$coef[2],m1.3$coef[2],m1.4$coef[2],m1.5$coef[2])
m1.se <- c(coef(summary(m1.1))[2,2],coef(summary(m1.2))[2,2],coef(summary(m1.3))[2,2],coef(summary(m1.4))[2,2],coef(summary(m1.5))[2,2])
m2.coef <- c(m2.1$coef[2],m2.2$coef[2],m2.3$coef[2],m2.4$coef[2],m2.5$coef[2])
m2.se <- c(coef(summary(m2.1))[2,2],coef(summary(m2.2))[2,2],coef(summary(m2.3))[2,2],coef(summary(m2.4))[2,2],coef(summary(m2.5))[2,2])
m3.coef <- c(m3.1$coef[2],m3.2$coef[2],m3.3$coef[2],m3.4$coef[2],m3.5$coef[2])
m3.se <- c(coef(summary(m3.1))[2,2],coef(summary(m3.2))[2,2],coef(summary(m3.3))[2,2],coef(summary(m3.4))[2,2],coef(summary(m3.5))[2,2])

# par(mar = c(4.1, 5.1, 1.1, 1.1))
# plot(1,type="n",xlim=c(0.8,5.2),ylim=c(-500,400), ylab=expression(paste("Effect on Deforestation (",m^{2} ," per " ,km^{2},")")),xlab="Year", cex.lab=1.2, cex.axis=1.2)
# abline(h=0, lty=2)
# polygon(x=c(year[1:5],year[5:1]),y=c(m1.coef+2*m1.se,m1.coef[5:1]-2*m1.se[5:1]),col=rgb(.6,.6,.6,0.5), border=NA)
# polygon(x=c(year[1:5],year[5:1]),y=c(m2.coef+2*m2.se,m2.coef[5:1]-2*m2.se[5:1]),col=rgb(0, 0, 0.8,0.5), border=NA)
# polygon(x=c(year[1:5],year[5:1]),y=c(m3.coef+2*m3.se,m3.coef[5:1]-2*m3.se[5:1]),col=rgb(0, 0, 1,0.5), border=NA)
# lines(year,m1.coef,type="l",col="black",lwd=5)
# lines(year,m2.coef,type="l",col="blue",lwd=5)
# lines(year,m3.coef,type="l",col="blue",lwd=5)

year <- 1:5

df_7 <- data.frame(
  year  = rep(year, 3),
  coef  = c(m1.coef, m2.coef, m3.coef),
  se    = c(m1.se,   m2.se,   m3.se),
  model = factor(rep(c("Model 1","Model 2","Model 3"),
                     each = length(year)))
) %>%
  mutate(
    ymin = coef - 2 * se,
    ymax = coef + 2 * se
  )


ggplot(df_7, aes(x = year, y = coef)) +

  # zero line
  geom_hline(yintercept = 0, linetype = 2) +

  # confidence bands
  geom_ribbon(aes(ymin = ymin, ymax = ymax, fill = model),
              alpha = 0.4, color = NA) +

  # coefficient lines
  geom_line(aes(color = model), linewidth = 1.8) +

  coord_cartesian(xlim = c(0.8, 5.2),
                  ylim = c(-500, 400)) +

  scale_fill_manual(values = c("grey60", "darkblue", "blue")) +
  scale_color_manual(values = c("black", "blue", "blue")) +

  labs(
    x = "Year",
    y = expression(paste("Effect on Deforestation (",
                         m^2, " per ", km^2, ")"))
  ) +

  theme_classic(base_size = 14) +
  theme(legend.position = "none")
```

2. Annotated Replication
After each subsequent code block, add some notes covering:

What does the code accomplish? (summary of the procedure or model)
What is the causal identification approach? (e.g., DiD, RDD, IV, matching)
What assumptions must hold for the estimates to be causally valid?
Are there any signs in the output that those assumptions are or are not satisfied?

## Evaluation

3. Critical Evaluation
Somewhere in the write-up (or as a closing section), address each of the following:

Causal identification: Is the identification strategy credible? What would have to be true for the estimates to be causal?
Statistical assumptions: Are key assumptions (parallel trends, exclusion restriction, etc.) tested or defended? Do you find the evidence convincing?
Sampling & external validity: Who is in the sample? To whom can results be generalized?
Measurement: Are the outcome and treatment variables measured accurately and without systematic bias?
Other limitations: Anything else that affects how much weight you would put on the study’s conclusions?



